A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-08-21 rr-flow.Rmd
supply metadata to papaja

---
title: "A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker"
shorttitle: "Reproducible Workflow"
author: "Aaron Peikert & Andreas M. Brandmaier"
date: "8/6/2019"
bibliography: Reproducible-Research.bib
output: html_document
---

@@

```{r abstract, child = 'abstract.Rmd'}
```

@@

@@

>>>>

---
title             : "A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker"
shorttitle        : "Reproducible Data Analysis Workflow"

author: 
  - name          : "Andreas Brandmaier"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Human Development, Lentzeallee 94, 14195 Berlin, Germany"
    email         : "brandmaier@mpib-berlin.mpg.de"
  - name          : "Aaron Peikert"
    affiliation   : "1,2"

affiliation:
  - id            : "1"
    institution   : "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
  - id            : "2"
    institution   : "Humboldt-Universität zu Berlin"

authornote: |

abstract: "`r readr::read_file('abstract.Rmd')`"

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["Reproducible-Research.bib"]

floatsintext      : yes
figurelist        : yes
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

@@

@@

\newpage

@@

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
